---
title: "Topic modeling"
author: "Yishun Zhang"
date: "2024-11-06"
output:
  html_document:
    df_print: paged
---

#Here’s how to perform topic modeling on movie plots in R using the topicmodels package, including data loading, text preprocessing, topic modeling (LDA), and visualization of each topic's common words.

#read the data:
```{r}
library(tidyr)
library(topicmodels)
library(dplyr)
library(tidyverse)
library(tm)
library(wordcloud)
library(ggwordcloud)
library(tidytext)
library(textrank)
library(ggforce)
movies<- read.csv("C:/Users/17756/Downloads/movie_plots_with_genres.csv")
movies<- movies%>% filter(!is.na(Plot))
```

```{r}

library(tidytext)
plot_word_counts <- movies%>%
  unnest_tokens(word, Plot)%>%
  count(Movie.Name, word, sort = TRUE)%>%
  ungroup()

# Create Document-Term Matrix (DTM).
plots_dtm <- plot_word_counts %>%
  cast_dtm(Movie.Name, word, n)

# Check dimensions of DTM.
dim(plots_dtm)
```

Creating LDA model.

```{r}
# Apply the LDA model, choose 30 topics.
set.seed(1066)
plots_lda <- LDA(plots_dtm, k = 30, control = list(seed = 1066))

# Creating beta matrix.
topics <- tidy(plots_lda, matrix = "beta")

# Identify the top terms for each topic
top_terms <- topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Print the top terms for each topic
print(top_terms)


```

Visualize top terms.

```{r}
top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap_paginate(~ topic, scales = "free_y", ncol = 3, nrow = 3, page = 1) + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::number_format(accuracy = 0.001)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Top Terms in Each Topic",
    x = "Probability",
    y = "Term"
  )

top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap_paginate(~ topic, scales = "free_y", ncol = 3, nrow = 3, page = 2) + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::number_format(accuracy = 0.001)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Top Terms in Each Topic",
    x = "Probability",
    y = "Term"
  )

top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap_paginate(~ topic, scales = "free_y", ncol = 3, nrow = 3, page = 3) + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::number_format(accuracy = 0.001)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Top Terms in Each Topic",
    x = "Probability",
    y = "Term"
  )

top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap_paginate(~ topic, scales = "free_y", ncol = 3, nrow = 3, page = 4) + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::number_format(accuracy = 0.001)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Top Terms in Each Topic",
    x = "Probability",
    y = "Term"
  )
```

After extracting top terms, working on the matrix, and doing the analysis.

```{r}
# Extract the document-topic distribution matrix (gamma values)
plots_gamma <- tidy(plots_lda, matrix = "gamma")

# Transform the document-topic matrix into a wide format for clustering
plots_gamma_wider <- plots_gamma %>%
  pivot_wider(names_from = topic, values_from = gamma)

# Perform K-means clustering on the document-topic distributions
set.seed(1234)
plots_gamma_wider_no_na <- plots_gamma_wider %>% drop_na()
cluster <- kmeans(plots_gamma_wider_no_na %>% select(-document), centers = 8)

# Visualize the clusters using a scatter plot
library(factoextra)
fviz_cluster(cluster, data = plots_gamma_wider_no_na %>% select(-document))

# Add the cluster assignments to the original dataset
plots_gamma_wider$cluster <- cluster$cluster

```

Achieve each cluster information (e.g. cluster 7, cluster 1).

```{r}
# Extract the list of movie titles in a specific cluster
cluster_7_names <- plots_gamma_wider %>%
  filter(cluster == 7) %>%
  pull(document)

cluster_1_names <- plots_gamma_wider %>%
  filter(cluster == 1) %>%
  pull(document)

# Display the movies
cluster_7_movies <- movies %>%
  filter(Movie.Name %in% cluster_7_names)

cluster_1_movies <- movies %>%
  filter(Movie.Name %in% cluster_1_names)

print(cluster_7_movies)
print(cluster_1_movies)
```

```{r}
# Function to generate a word cloud for each topic
generate_wordcloud <- function(topic_number, topics_data) {
  # Filter terms for the specified topic
  topic_terms <- topics_data %>%
    filter(topic == topic_number) %>%
    arrange(desc(beta)) %>%
    slice_max(beta, n = 10) # Select top 30 words
  
  # Generate the word cloud
  wordcloud(words = topic_terms$term,
            freq = topic_terms$beta,
            max.words = 10,
            random.order = FALSE,
            colors = brewer.pal(8, "Dark2"),
            scale = c(4, 0.5))
}

# Generate word clouds for each topic (Example: first 5 topics)
par(mfrow = c(2, 3)) # Set up a layout to display multiple word clouds
for (i in 1:5) {
  generate_wordcloud(i, topics)
  title(paste("Topic", i))
}
```









